---
title: "DriveTime App Pitch"
author: "Kim"
date: "11/04/2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rgeos)
library(osrm)
library(leaflet)
```

## Where should we go for the weekend? 

- Know how long you're willing to drive
- Know where you are
- How do you figure out what the possibilities are?

## DriveTimes shows equal driving times

- Uses Open Street Map routing service
- Needs 5 inputs from the user
    - Start location (lat/long coordinate)
    - Minimum drive time
    - Maximum drive time
    - Increments to calculate

## Behind the Scenes I
- Calculates a travel matrix
- Creates polygons of equal drive times

```{r travelmatrix, echo = TRUE}
isodat <- osrmIsochrone(loc = c(-115.176, 36.151), breaks = seq(180, 240, 30))
timebreaks <- seq(180, 240, 30)
faclevels <- c(paste(0, "to", timebreaks[1], "min"), paste(timebreaks[-length(timebreaks)], "to", timebreaks[-1], "min"))
isodat@data$drive_times <-  factor(paste(isodat@data$min, "to", isodat@data$max, "min"), levels = faclevels)
print(isodat@data)
```

## Behind the Scenes II
- Displays using the leaflet package

```{r display}
factpal <- colorFactor(rev(heat.colors(length(timebreaks))), isodat@data$drive_times)
leaflet() %>% 
            setView(-115.176, 36.151, zoom = 7) %>%
            addProviderTiles("CartoDB.Positron", group="Greyscale") %>% 
            addMarkers(lng = -115.176, lat = 36.151, popup = "Start Location") %>% 
            addPolygons(fill=TRUE, stroke=TRUE, color = "black",
                        fillColor = ~factpal(isodat@data$drive_times),
                        weight=0.5, fillOpacity=0.2,
                        data = isodat, popup = isodat@data$drive_times,
                        group = "Drive Time") %>% 
            # Legend
            addLegend("bottomright", pal = factpal, values = isodat@data$drive_time,   title = "Drive Time")

```

